### 2014-08-18 analysis/context_permeability.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

@@

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/context_permeability/regular_networks/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```
We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and number of networks**.

```{r message=FALSE}
require(reshape)
require(tables)

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))

fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("num.networks", "k", "value")

 #create a pretty table for latex
latex_table <- tabular(cast(fcdata_table, num.networks~k, value="value"))

@@

#I can also save this table to a file for later reference
latex(latex_table,file="tex/regular_convergence.tex", booktabs=T, )
```

This table shows the percentage of simulation runs that converged to total consensus over 100 
independent runs.

# Number of Encounters for K-Regular Networks 
Now we analise the number of encouters necessary to achieve consensus. Or the total number of encounters that 
were performed if consensus was not achieved. **The maximum number of simulation cycles is 2000.** The maximum
number of encounters is thus limited by the maximum number of simulation cycles (and in consequense steps). The 
data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/context_permeability/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for how many networks were in the simulation and what was the k value we 
can merge the data like we have done previously. 
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

We now filter some of the variables out.
```{r message=FALSE}
#filter some things out
fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
head(fedata)

#filter encounter data include only num networks > 3
fedata_net1 <- fedata[fedata$num.networks>2 & fedata$network.0.k <= 5,]

fedata_net10 <- fedata[fedata$num.networks>2 & fedata$network.0.k > 5,]

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~num.networks, c(mean, sd))

Hmisc::latex(fedata_table_full, file="tex/regular_encounters_full.tex",booktabs=T)
```

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.

```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$num.networks), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")

plot
```

To try to answer the question "why do some outliers show up in the data" (simulation runs that took more time than the typical run), I look at the outlier from the configuration **(networks=3, k = 10)**. What I'm trying to find is weather the network structure is the same from the other runs.

```{r}
source("../R/read_network.R")

network_data <- fread("../data/context_permeability/regular_networks/networks.csv")

@@

@@

#outlier network properties
outlier_net_props <- read.composite.properties(outlier_net)
normal_net_props <- read.composite.properties(normal_net)

@@

```{r}
opinion_data <- read.opinion.progress("../data/context_permeability/regular_networks/opinion_progress.csv")
#filter opinion to outlier run and normal run
outlier_run <- opinion_data[opinion_data$"cfg.id" == outlier$"cfg.id" & opinion_data$"run" == outlier$"run",]
normal_run <- opinion_data[opinion_data$"cfg.id" == normal$"cfg.id" & opinion_data$"run" == normal$"run",]

@@

plot_run_normal + labs(title = "Normal Run")
plot_run_outlier + labs(title = "Outlier Run")
```

@@

We first look at the number of convergences to total consensus in 100 simulation runs. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/context_permeability/scale-free_networks/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

@@

```{r}
require(reshape)
require(tables)

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.d, FUN=sum)
colnames(fcdata_table) <- c("num.networks", "d", "value")

@@

# Number of Encounters for Scale-Free Networks #
Now we analise the number of encouters necessary to achieve consensus. Or the total number of encounters that 
were performed if consensus was not achieved. The data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/context_permeability/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for how many networks were in the simulation and what was the **d** value, we 
can merge the data like we have done previously. 
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

@@

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **d = {1,2,3,4,5}**. We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.

@@

@@

@@

# Convergence for Heterogeneous Configuration (K-Regular Network + Scale-free Network) #
Now we analyse what happens when we use an heterogenous configuration, this is, each layer in the model uses different 
network models. In a first experiment, we use a K-Regular network for one layer and a Scale-free network for the other. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/context_permeability/scale-free_regular/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

@@

```{r message=FALSE}
require(reshape)
require(tables)

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("d", "k", "value")

@@

This table shows the percentage of simulation runs that converged to total consensus over 100 
independent runs.

# Number of Encounters for Heterogeneous Configuration (K-Regular Network + Scale-free Network) #
In this section, we analise the number of encouters necessary to achieve consensus with this heterogenous setup.
The data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/context_permeability/scale-free_regular/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for the d and k values we can merge the data with the parameter space
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

@@

@@

@@

plot
```

@@

@@

```{r}
source("../R/read_network.R")
network_data <- fread("../data/context_permeability/scale-free_regular/networks.csv")
#filter the data, we just need the data from one simulation run
network_data <- network_data[network_data$"cfg.id" == fedata_net10[1,]$"cfg.id" & network_data$"run" == fedata_net10[1,]$"run",]

k_regular_network <- read.single.network(data=network_data, layer=0)
scale_free_network <- read.single.network(data=network_data, layer=1)
combined_network <- k_regular_network + scale_free_network

@@

par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular Network")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Scale-Free with D = 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined Networks")
```

@@

```{r fig.width=15}
par(mfrow=c(1,3))
plot.degree.distribution(network=k_regular_network, "10-Regular Network")
plot.degree.distribution(network=scale_free_network, "Scale-Free Network with D = 2")
plot.degree.distribution(network=combined_network, "Combined network")
```

@@

## CONVERGENCE FOR REG/SF/SF ##

```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_scale-free_regular/param-space_2014-05-30_18:43:13experiment:2_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/context_permeability/scale-free_scale-free_regular/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

@@

```{r message=FALSE}
require(reshape)
require(tables)

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","network.0.k","network.1.d", "network.2.d"), measure.vars=c("consensus-achieved"))

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("d", "k", "value")

@@

This table shows the percentage of simulation runs that converged to total consensus over 100 
independent runs.

@@

Hmisc::latex(fedata_table_full, file="tex/regular_scale-free_scale_free_encounters_full.tex",booktabs=T)
```

@@

plot
```

@@

>>>>

We will start by loading the dependencies for this report.
```{r}
source("../R/read_network.R")
source("../R/experiment_utils.R")

library(data.table)
library(reshape2)
library(reshape)
library(tables)

library(ggplot2)
#to display ggplot2 plots in a grid layout
library(gridExtra)
```

@@

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
```{r results='asis',message=FALSE}

#read the convergence data
params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/convergence/param-space_2014-08-01_00:09:09experiment:0_.csv")

#read the adata related to consensus was achieved before

convergence_data <- fread("../data/context_permeability/regular_networks/convergence/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")

convergence_data <- melt(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))

convergence_data <- aggregate(data=convergence_data, convergence_data$value~convergence_data$num.networks + convergence_data$network.0.k, FUN=function(x) sum(x)/length(x))

colnames(convergence_data) <- c("networks", "k", "convergence")
head(convergence_data)

table <- cast(convergence_data, networks~k, value="convergence")
latex_table <- tabular.cast_df(table)
```
We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and number of networks**.

#save this table to a file for later reference
Hmisc::latex(latex_table, file="tex/regular_convergence.tex",booktabs=T)
```

This table shows the convergence ratio to total consensus for 3000 independent runs.

# Number of Encounters for K-Regular Networks 
Now we analise the number of encouters necessary to achieve consensus. Or the total number of encounters that 
were performed if consensus was not achieved. **The maximum number of simulation cycles is 2000.** The maximum
number of encounters is thus limited by the maximum number of simulation cycles (and in consequense steps). The 
data for the encounters contains the following variables.
```{r}
params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-07-23_11:40:44experiment:0_.csv")

encounter_data <- fread("../data/context_permeability/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for how many networks were in the simulation and what was the k value we 
can merge the data like we have done previously. 
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

We now filter some of the variables out.
```{r message=FALSE}
#filter some columns that are not needed and convert to melted format
fedata <- melt(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
head(fedata)

#divide data in two partitions k<=5 and k>5
fedata_net1 <- fedata[fedata$num.networks>2 & fedata$network.0.k <= 5,]
fedata_net10 <- fedata[fedata$num.networks>2 & fedata$network.0.k > 5,]

#create a table with avg and stdev
cast_fedata_table <- cast(data=fedata, formula=network.0.k~num.networks, c(mean, sd))
fedata_table_full <- tabular.cast_df(cast_fedata_table)
```

Display the table in HTML for the knitr report and save it to a file.
```{r results='asis',message=FALSE}
#to print the table created with tabular
html(fedata_table_full)

#print this to a file to use in the paper
Hmisc::latex(fedata_table_full, file="tex/regular_encounters_full.tex",booktabs=T)
```

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks >= 3** since less networks lead to much worse results. As we have seen in the previous convergence results.
```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$num.networks), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_kregular_12345.pdf"), width=7, height=5)
plot
dev.off()

pdf(paste("./pdf/","context_permeability_encounters_kregular_1020304050.pdf"), width=7, height=5)
plot
dev.off()

@@

To try to answer the question "why do some outliers show up in the data" (simulation runs that took more time than the typical run), I look at the outlier from the configuration **(networks=3, k = 10)**. What I'm trying to find is weather the network structure is the same from the other runs. 
```{r}
network_data <- fread("../data/context_permeability/regular_networks/networks.csv")

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_kregular_k10_outlier.pdf"), width=7, height=5)
plot
dev.off()

@@

#outlier network properties
outlier_net_props <- read.composite.properties(outlier_net)
normal_net_props <- read.composite.properties(normal_net)
```

@@

```{r}
opinion_data <- read.opinion.progress("../data/context_permeability/regular_networks/opinion_progress.csv")

#filter opinion to outlier run and normal run
outlier_run <- opinion_data[opinion_data$"cfg.id" == outlier$"cfg.id" & opinion_data$"run" == outlier$"run",]
normal_run <- opinion_data[opinion_data$"cfg.id" == normal$"cfg.id" & opinion_data$"run" == normal$"run",]

@@

plot_run_normal + labs(title = "Normal Run")
plot_run_outlier + labs(title = "Outlier Run")

#print to pdf
pdf(paste("./pdf/","context_permeability_simrun_kregular_k10_normal.pdf"), width=7, height=5)
plot_run_normal + labs(title = "Normal Run")
dev.off()

pdf(paste("./pdf/","context_permeability_simrun_kregular_k10_outlier.pdf"), width=7, height=5)
plot_run_outlier + labs(title = "Outlier Run")
dev.off()
```

We now look at the average difference between the memory of opinions seen. This is abs(number of opinion 1 seen - number of opinion 2 seen). We also look at the variance of this difference between the 100 agents.
```{r}
#check the opinion memory difference for the outlier and the normal run
plot.op.diff <- function(current_run){

  average_data <- melt(current_run, id=(c("step")), measure.vars=(c("avg-op-diff")))

  .e <- environment()

  average_plot <- ggplot(data = average_data, aes(x = average_data$step, y = average_data$value), environment=.e)
  average_plot <- average_plot + geom_line() + geom_point(size=0)
  average_plot <- average_plot + labs(x = "Simulation Step", y = "Average Memory Difference")

  #average_plot <- average_plot + labs(title = "Average Opinion Memory Difference")
  average_plot <- average_plot + theme_bw()
  average_plot <- average_plot + theme(legend.title=element_blank())

  #plot variance

  variance_data <- melt(current_run, id=(c("step")), measure.vars=(c("variance-op-diff")))

  variance_plot <- ggplot(data = variance_data, aes(x = variance_data$step, y = variance_data$value), environment=.e)
  variance_plot <- variance_plot + geom_line() + geom_point(size=0)
  variance_plot <- variance_plot + labs(x = "Simulation Step", y = "Variance of Opinion Memory Difference")

  #variance_plot <- variance_plot + labs(title = "Variance of Opinion Memory Difference")
  variance_plot <- variance_plot + theme_bw()
  variance_plot <- variance_plot + theme(legend.title=element_blank())

  grid.arrange(average_plot, variance_plot, ncol=2)
}
```

Bellow we can see the average difference between opinion memory 
in the first ten steps (which was when the simulation converged for the "normal" run).
```{r}
current_run <- normal_run
current_run <- current_run[current_run$"step" <= 10,]

plot.op.diff(current_run)

pdf(paste("./pdf/","cp-regular-normal-run-memory-diff.pdf"), width=15, height=5)
plot.op.diff(current_run)
dev.off()

For the outlier run we get the following results. We can see that the average difference in the opinion memory rises more quickly for the normal run than it does in the outlier run. The values of opinion memory and the position of the agents in the network is such that the convergence is slower but steady towards total consensus.
```{r}
current_run <- outlier_run
current_run <- current_run[current_run$"step" <= 10,]
plot.op.diff(current_run)

pdf(paste("./pdf/","cp-regular-outlier-run-memory-diff.pdf"), width=15, height=5)
plot.op.diff(current_run)
dev.off()
```

In the outlier run the variance for the opinion difference is also quite low from **step 0 to 25**, this  indicates that while opinion memory difference is increasing on average, there is no significant difference between agents in terms of their counters. **There is no particular group of agents that is more strongly inclined to one particular opinion.** From this point on, the memory difference variance grows exponentialy --this corresponds to the point where one opinion won over the other and convergence towards consensus begins.

```{r}
current_run <- outlier_run
current_run <- current_run[current_run$"step" <= 100,]
plot.op.diff(current_run)

pdf(paste("./pdf/","cp-regular-outlier-0-100-memory-diff.pdf"), width=15, height=5)
plot.op.diff(current_run)
dev.off()
```

```{r}

current_run <- outlier_run
plot.op.diff(current_run)

pdf(paste("./pdf/","cp-regular-outlier-fullrun-memory-diff.pdf"), width=15, height=5)
plot.op.diff(current_run)
dev.off()

@@

We first look at the convergence ratio in 3000 independent simulation runs. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/convergence/param-space_2014-08-01_00:47:12experiment:0_.csv")

#read the adata related to consensus was achieved before 
library(data.table)
convergence_data <- fread("../data/context_permeability/scale-free_networks/convergence/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

@@

```{r}

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.d, FUN=function(x) sum(x)/length(x))
colnames(fcdata_table) <- c("num.networks", "d", "value")

@@

# Number of Encounters for Scale-Free Networks #
Now we analise the number of encouters necessary to achieve consensus. Or the total number of encounters that 
were performed if consensus was not achieved. The data for the encounters contains the following variables.
```{r}
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")

encounter_data <- fread("../data/context_permeability/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for how many networks were in the simulation and what was the **d** value, we 
can merge the data like we have done previously. 
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

@@

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **d = {1,2,3,4,5}**. We look at **configurations with a number of networks >= 3** which shows the best results in terms of convergence.

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_sf.pdf"), width=7, height=5)
plot
dev.off()

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_sf_best.pdf"), width=7, height=5)
plot
dev.off()

@@

# Convergence for Heterogeneous Configuration (K-Regular Network + Scale-free Network) #
Now we analyse what happens when we use an heterogenous configuration, this is, each layer in the model uses different 
network models. In a first experiment, we use a K-Regular network for one layer and a Scale-free network for the other. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/convergence/param-space_2014-08-01_11:57:13experiment:2_.csv")

#read the adata related to consensus was achieved before

convergence_data <- fread("../data/context_permeability/scale-free_regular/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

@@

```{r message=FALSE}

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=function(x) sum(x)/length(x))
colnames(fcdata_table) <- c("d", "k", "value")

@@

This table shows the ratio convergence to total consensus over 3000 simulation runs.

# Number of Encounters for Heterogeneous Configuration (K-Regular Network + Scale-free Network) #
In this section, we analise the number of encouters necessary to achieve consensus with this heterogenous setup.
The data for the encounters contains the following variables.
```{r}
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
encounter_data <- fread("../data/context_permeability/scale-free_regular/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for the d and k values we can merge the data with the parameter space
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

@@

fedata_table_full <- tabular(cast_fedata_table)
```

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_sfreg_k12345.pdf"), width=7, height=5)
plot
dev.off()

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_sfreg_k1020304050.pdf"), width=7, height=5)
plot
dev.off()
```

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_sfreg_k1020304050_best.pdf"), width=7, height=5)
plot
dev.off()
```

@@

```{r}
network_data <- fread("../data/context_permeability/scale-free_regular/networks.csv")
#filter the data, we just need the data from one simulation run
network_data <- network_data[network_data$"cfg.id" == fedata_net10[1,]$"cfg.id" & network_data$"run" == fedata_net10[1,]$"run",]

k_regular_network <- read.single.network(data=network_data, layer=0)
scale_free_network <- read.single.network(data=network_data, layer=1)
combined_network <- k_regular_network + scale_free_network
```

@@

par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular Network")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Scale-Free with D = 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined Networks")

#print to pdf
pdf(paste("./pdf/","network_properties_10regular_2scale-free.pdf"), width=15, height=5)
par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular Network")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Scale-Free with D = 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined Networks")
dev.off()
```

@@

```{r fig.width=15}
par(mfrow=c(1,3))
plot.degree.distribution(network=k_regular_network, "10-Regular Network")
plot.degree.distribution(network=scale_free_network, "Scale-Free Network with D = 2")
plot.degree.distribution(network=combined_network, "Combined network")

pdf(paste("./pdf/","network_properties_10regular_2scale-free_degree_dist.pdf"), width=15, height=5)
par(mfrow=c(1,3))
plot.degree.distribution(network=k_regular_network, "10-Regular Network")
plot.degree.distribution(network=scale_free_network, "Scale-Free Network with D = 2")
plot.degree.distribution(network=combined_network, "Combined network")
dev.off()
```

@@

## CONVERGENCE FOR REG/SF/SF ##
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_scale-free_regular/param-space_2014-05-30_18:43:13experiment:2_.csv")

#read the adata related to consensus was achieved before 
convergence_data <- fread("../data/context_permeability/scale-free_scale-free_regular/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

@@

```{r message=FALSE}
#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","network.0.k","network.1.d", "network.2.d"), measure.vars=c("consensus-achieved"))

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=function(x) sum(x)/length(x))
colnames(fcdata_table) <- c("d", "k", "value")

 #create a table for latex
latex_table <- tabular(cast(fcdata_table, d~k, value="value"))
```

Display the table in html and print it to a file:
```{r results='asis'}
html(latex_table)

@@

This table shows the convergence ratio to total consensus over 100 simulation runs.

@@

#split the data into two partitions k<=5 and k>5
fedata_net1 <- fedata[fedata$network.0.k <= 5,]
fedata_net10 <- fedata[fedata$network.0.k > 5,]

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~network.1.d, c(mean, sd))
fedata_table_full <- tabular(cast_fedata_table)
```

Create the tables:
```{r results='asis',message=FALSE}
#to print the table created with tabular
html(fedata_table_full)

#print this to a file to use in the paper
Hmisc::latex(fedata_table_full, file="tex/regular_scale-free_scale_free_encounters_full.tex",booktabs=T)
```

@@

#print to pdf
pdf(paste("./pdf/","context_permeability_encounters_reg_sf_sf_k12345.pdf"), width=7, height=5)
plot
dev.off()

@@

pdf(paste("./pdf/","context_permeability_encounters_reg_sf_sf_k1020304050.pdf"), width=7, height=5)
plot
dev.off()
```

Focusing now on the best performing configurations and on the runs that produced a convergence in less than 50000 encounters, the distribution of the number of encounters is as follows. 
```{r}
fedata_net10 <- fedata_net10[fedata_net10$"network.1.d" > 1 & fedata_net10$value <= 10000,]

pdf(paste("./pdf/","context_permeability_encounters_reg_sf_sf_best.pdf"), width=7, height=5)
plot
dev.off()
```
